Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-06 WSSSPE1_report/WSSSPE1_summary_report.tex
Adding back in some of the subsections to software
Some reordering of text and discussion, fitting in the main text
with the overall themes of the discussion in order to make it easier
to read through the section.

The panel on developing and supporting software examined the challenges
around scientific software development and support, mainly focused on research
groups that also produce code in various forms. There was widespread agreement
that developing and maintaining software is hard, but best practices can help.
Several participants stated that documentation is not just for users, and paying attention
to API documentation, tutorials for building and deploying software, along with
documented development practices can be very helpful in bringing  new developers
into a project efficiently.

@@

Communities are extremely important in software projects, and both their
building and continued engagement need attention during the project life cycle.
Several of the submitted papers discussed how communities have been built around
projects, and what is needed to enable a project to grow. Among these are public
source code hosting, mailing lists, documentation, wikis, bug trackers, software
downloads, continuous integration, software quality dashboards, and of course,
a general web presence to tie all of these things together. Questions were posed
around users not answering the questions of other users. Several participants
offered counterexamples, such as mailing lists where developers do not participate
as much due to users being more active, or whether the ``core
team'' can end up setting unrealistic expectations by doing too much. Team Geek~\cite{opac-b1134063}
and Turk's paper on scaling code in the human dimension~\cite{Turk:2013:SCH:2484762.2484782}  discuss how development
lists that are welcoming to people actually have many more people contributing.

@@

@@

@@

@@

>>>>

The panel on developing and supporting software examined the challenges
around scientific software development and support, mainly focused on research
groups that also produce code in various forms. There was widespread agreement
that developing and maintaining software is hard, but best practices can help.
Several participants added that documentation is not just for users, and writing
API documentation, tutorials for building and deploying software, along with
documented development practices can be very helpful in bringing  new developers
into a project efficiently.

\subsection{Research or Reuse?}

@@

\subsection{Communities and Career Paths}

Communities are extremely important in software projects, and both their
building and continued engagement need attention during the project life cycle.
Several of the submitted papers discussed how communities have been built around
projects, and what is needed to enable a project to grow. Among these are public
source code hosting, mailing lists, documentation, wikis, bug trackers, software
downloads, continuous integration, software quality dashboards, and of course,
a general web presence to tie all of these things together.

There was extended discussion about users not answering the questions of other
users. Several participants
offered counterexamples, such as mailing lists where developers do not participate
as much due to users being more active, or whether the ``core
team'' can end up setting unrealistic expectations by doing too much. Team Geek~\cite{opac-b1134063}
and Turk's paper on scaling code in the human dimension~\cite{Turk:2013:SCH:2484762.2484782}  discuss how development
lists that are welcoming to people actually have many more people contributing.

@@

\subsection{Defining Sustainability for Scientific Software}

@@

\subsection{Software Process, Code Review, Automation, Reproducibility}

@@

\subsection{Training Scientists to Develop and Support Software}

@@

\subsection{Funding, Sustainability Beyond the First Grant/Institution}
